---
title: "ue6"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Get the packages
```{r}

```

All packages that we know are made out of functions. If we use `View()` we can find out more about how functions are made:

```{r}
View(read.table)
```


Let's define a simple function:

```{r}

```

# Funktion zum Einlesen von Whatsapp-Chats bauen:
```{r}




```


# Test it
```{r}

}
```



# Let's clean our dataset from last week

We have the information of the release year in the same column like the movie title
```{r}

```

We cannot simply separate by spaces as they appear throughout our observation. Therefore we will need to do it another way.
In the first try we will use a simple separate function:
```{r}

```
That didn't really work...


Let's define a function where we will look for the first bracket of our year string. We will append it with a substring that clearly marks the separating point of our observation
```{r}

```


Let's test our function:
```{r}

```


```{r}

```
Mit dieser Funktion fahren wir am sichersten!


At last we want to source another R script in our current one:
```{r}

```

