---
title: "ue3"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Include Packages
```{r}

```

# Import the Black Friday dataset
```{r}

```


# Let's get an overview first!
```{r}

```


Piping operator shortcut
%>% -> "ctrl + shift + m"

Drop duplicate rows from data as they impact the analysis!
```{r}

```

# Tasks for today


Create a new dataframe that contains all customers from the age group "18-25".
We only want to observe the gender,
                          occupation, 
                          and the number of purchases made at each product category. 
Sort the dataframe in descending order by "Occupation".


```{r}


  
```

  
Now we want to find the strongest consumer. We create a new column "product_sum" that contains the sum of all values from the product categories.

```{r}

```

We do the same for the age group "46-50"

```{r}

```





Create a summary of all age groups that shows their average purchase power of product category 2.
```{r}

```



Now a different use case: We want to find the average lifetime each age group has spent in the observed city.
```{r}


```


```{r}

```


