---
title: "ue4"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Transform 2

Get the packages
```{r}

library(tidyverse)
```

Import data
```{r}
data <- read_csv("BlackFriday.csv")
```


```{r}
data[is.na(data)]<- 0
data <- data %>% unique()
```



We transform all columns with `mutate_all()`. The same operation will be executed on all data.
```{r}
products_transformed <- data %>% 
  select(9:11) %>% 
  mutate_all(sqrt) %>% 
  mutate_all(log1p)

products_transformed <- data %>% 
  select(9:11) %>% 
  mutate_all(funs(sqrt,log1p))
             

```

We can also select a few columns instead:
```{r}
product_spot_transformed <- data %>% 
  mutate_at(vars(9:10), '/', 100)

head(product_spot_transformed)

```



Or we make a conditional mutation:
```{r}
products_if_transformed <- data %>% 
  mutate_if(is.numeric, "/", 100)

head(products_if_transformed)

```



The same logic goes with `summarise_at` and `summarise_if`:
```{r}
product_summarized <- data %>% 
  group_by(Age) %>% 
  summarise_at(c("Product_Category_1","Product_Category_2","Product_Category_3"), mean, na.rm = TRUE)
```


```{r}
data %>% group_by(Age) %>% 
  summarise_if(is.numeric, mean) %>% 
  arrange(desc(Age))
```

Finally, we want to ungroup our data again:
```{r}

ungroup(data)
```

# Regular Expression

If we want to replace a character in a string, we simply use the `sub()` function. However, this command doesn't work for arithmetic operations. In regular expressions, arithmetic operators stand for other commands. Here an example of a problem we could deal with:

```{r}

string <- "I need a t-shirt with size XXL"
string <- sub("XXL", "L", string)


regex_string <- "27 + 5 = 22"
regex_string <- sub("\\+", "-", regex_string)
```





Now let's move on with some higher-level RegEx. We therefore need the package `stringr`:
```{r}
library(stringr)

```


At last, we want to create a dataframe from a single string. This is an academic example and is for better understanding of dataframes and lists in R:
```{r}

your_text <-"omg~dis~txt!hav~no~delims!or~ln~brks"
write(your_text, "text_file.txt");
rm(your_text)

eol_str = "!"
sep_str = "~"

row_list <- scan("text_file.txt", what=character(), sep=eol_str) %>% 
  strsplit(split=sep_str)

View(row_list)

df <- data.frame(row_list)
df <- data.frame(t(df), row.names = NULL)
head(df)

```






