---
title: "ue4"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Transform 2

Get the packages
```{r}


```

Import data
```{r}

```


```{r}


```



We transform all columns with `mutate_all()`. The same operation will be executed on all data.
```{r}




```

We can also select a few columns instead:
```{r}


```



Or we make a conditional mutation:
```{r}


```



The same logic goes with `summarise_at` and `summarise_if`:
```{r}


```


```{r}

```

Finally, we want to ungroup our data again:
```{r}
```

# Regular Expression

If we want to replace a character in a string, we simply use the `sub()` function. However, this command doesn't work for arithmetic operations. In regular expressions, arithmetic operators stand for other commands. Here an example of a problem we could deal with:

```{r}


```





Now let's move on with some higher-level RegEx. We therefore need the package `stringr`:
```{r}


```


At last, we want to create a dataframe from a single string. This is an academic example and is for better understanding of dataframes and lists in R:
```{r}



```






